Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection Fourier transform Mass Spectrometry Experiments

### 2022-05-13 doc/peakcharacterization_manuscript.Rmd
added section numbers so we match what is in the MDPI version

::: {custom-style="MDPI_2.1_heading1"}
## Introduction
:::

@@

::: {custom-style="MDPI_2.1_heading1"}
## Results
:::

::: {custom-style="MDPI_2.2_heading2"}
### Naïvely Averaged Data Have Bad Relative Intensities
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### m/z to Frequency
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Sliding Window Density to Remove Noise
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Peak Characterization Using Quadratic Fit
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Breaking Up Initial Regions
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Normalization of Scans
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Mitigation of High Peak Density Artifacts
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Changes in Relative Standard Deviation (RSD)
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Difference to Relative Natural Abundance
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Method Specific Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Changes in P-Values On a Large Dataset
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Quality Control and Quality Analysis
:::

@@

::: {custom-style="MDPI_2.1_heading1"}
## Discussion
:::

@@

::: {custom-style="MDPI_2.1_heading1"}
## Materials and Methods
:::

::: {custom-style="MDPI_2.2_heading2"}
### Samples and Overall Processing
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Matching Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Conversion of m/z to Frequency
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Frequency Intervals
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Interval Range Based Data
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Peak Containing Intervals
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Peak Detection and Centroided Values
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Scan to Scan Normalization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Full Scan-Centric Characterization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Correction of Height and Standard Deviation
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Marking High Frequency Standard Deviation Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Calculation of Relative Standard Deviation
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Scan-Centric Peak Assignment
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Consistently Assigned Lipid Spectral Feature (Corresponded Peak) Generation and Peak Intensity Normalization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Peak - Peak NAP Height Ratios
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Differential Analysis of Large Dataset
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Software Used
:::

>>>>

::: {custom-style="MDPI_2.1_heading1"}
## 1. Introduction
:::

@@

::: {custom-style="MDPI_2.1_heading1"}
## 2. Results
:::

::: {custom-style="MDPI_2.2_heading2"}
### 2.1 Naïvely Averaged Data Have Bad Relative Intensities
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.2 m/z to Frequency
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.3 Sliding Window Density to Remove Noise
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.4 Peak Characterization Using Quadratic Fit
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.5 Breaking Up Initial Regions
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.6 Normalization of Scans
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.7 Mitigation of High Peak Density Artifacts
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.8 Changes in Relative Standard Deviation (RSD)
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.9 Difference to Relative Natural Abundance
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.10 Method Specific Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.11 Changes in P-Values On a Large Dataset
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.12 Quality Control and Quality Analysis
:::

@@

::: {custom-style="MDPI_2.1_heading1"}
## 3. Discussion
:::

@@

::: {custom-style="MDPI_2.1_heading1"}
## 4. Materials and Methods
:::

::: {custom-style="MDPI_2.2_heading2"}
### 4.1 Samples and Overall Processing
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.2 Matching Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.3 Conversion of m/z to Frequency
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.4 Frequency Intervals
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.5 Interval Range Based Data
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.6 Peak Containing Intervals
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.7 Peak Detection and Centroided Values
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.8 Scan to Scan Normalization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.9 Full Scan-Centric Characterization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.10 Correction of Height and Standard Deviation
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.11 Marking High Frequency Standard Deviation Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.12 Calculation of Relative Standard Deviation
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.13 Scan-Centric Peak Assignment
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.14 Consistently Assigned Lipid Spectral Feature (Corresponded Peak) Generation and Peak Intensity Normalization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.15 Peak - Peak NAP Height Ratios
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.16 Differential Analysis of Large Dataset
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.17 Software Used
:::
